Arterial pulsations are not powerful enough to drive perivascular drainage of solutes from the brain

### 2017-01-11 paper.tex
added reynolds number to numerical section

In order to obtain the input functions $R_i(z,t)$ and $p_z$ for the analytical model developed in the previous section, a section of human MCA was modelled as a 1D axisymmetric tube in a cylindrical coordinate system with cross-sectional lumen area $A(z,t)$ and flux $q(z,t)$ using the Python package VaMpy \cite{Diem2016a}. The geometry parameters are listed in \autoref{tab:geometry}. Following the derivations in \cite{Olufsen2000,Diem2016} arteries are represented by the conservation law
\begin{equation}
  \frac{\dd \boldsymbol{U}}{\dd t} + \frac{\dd \boldsymbol{F}}{\dd z} = \boldsymbol{S}, \label{eq:conservation}
\end{equation}
where
\begin{gather*}
  \boldsymbol{U} = \begin{pmatrix} A(z,t) \\ q(z,t) \end{pmatrix}, \quad \boldsymbol{F} = \begin{pmatrix} q(z,t)\\ \dfrac{q(z,t)^2}{A(z,t)} + f(r_0) \sqrt{A_0(z) A(z,t)} \end{pmatrix}, \quad \boldsymbol{S} = \begin{pmatrix} 0\\ S_1 \end{pmatrix}\\
  \begin{split}
    S_1 = -&\frac{2 \pi R(z,t)}{\delta_b \mathrm{Re}} \frac{q(z,t)}{A(z,t)} +\\
    &\left( 2 \sqrt{A(z,t)} \left( \sqrt{\pi} f(r_0) + \sqrt{A_0(z)} \frac{df(r_0)}{dr_0 } \right) - A(z,t) \frac{df(r_0)}{dr_0} \right) \frac{dr_0(z)}{dz}.
  \end{split}
\end{gather*}
Elasticity of the artery wall is modelled via the quantity $f(r_0) = 4Eh/(3r_0)$. The relationship $Eh/r_0$ is based on compliance estimates
\begin{equation}
  \frac{Eh}{r_0} = k_1 \exp \left( k_2 r_0(z) \right) + k_3
\end{equation}
with $k_1, k_2, k_3$ constants \cite{Olufsen2000}. To derive \eqref{eq:conservation} it was necessary to make assumptions about the velocity profile of blood flow through an artery. Blood flow is considered pulsatile laminar and vessels are considered slightly tapered, therefore the velocity profile is assumed to be mostly flat with a thin boundary layer $\delta_b = (\nu T/(2\pi))^{0.5}$, such that $\delta_b \ll R(z,t)$ \cite{Olufsen2000}.

@@

>>>>

In order to obtain the input functions $R_i(z,t)$ and $p_z$ for the analytical model developed in the previous section, a section of human MCA was modelled as a 1D axisymmetric tube in a cylindrical coordinate system with cross-sectional lumen area $A(z,t)$ and flux $q(z,t)$ using the Python package VaMpy \cite{Diem2016a}. The geometry parameters are listed in \autoref{tab:geometry}. Following the derivations in \cite{Olufsen2000,Diem2016} arteries are represented by the conservation law
\begin{equation}
  \frac{\dd \boldsymbol{U}}{\dd t} + \frac{\dd \boldsymbol{F}}{\dd z} = \boldsymbol{S}, \label{eq:conservation}
\end{equation}
where
\begin{gather*}
  \boldsymbol{U} = \begin{pmatrix} A(z,t) \\ q(z,t) \end{pmatrix}, \quad \boldsymbol{F} = \begin{pmatrix} q(z,t)\\ \dfrac{q(z,t)^2}{A(z,t)} + f(r_0) \sqrt{A_0(z) A(z,t)} \end{pmatrix}, \quad \boldsymbol{S} = \begin{pmatrix} 0\\ S_1 \end{pmatrix}\\
  \begin{split}
    S_1 = -&\frac{2 \pi R(z,t)}{\delta_b \mathrm{Re}} \frac{q(z,t)}{A(z,t)} +\\
    &\left( 2 \sqrt{A(z,t)} \left( \sqrt{\pi} f(r_0) + \sqrt{A_0(z)} \frac{df(r_0)}{dr_0 } \right) - A(z,t) \frac{df(r_0)}{dr_0} \right) \frac{dr_0(z)}{dz}.
  \end{split}
\end{gather*}
Elasticity of the artery wall is modelled via the quantity $f(r_0) = 4Eh/(3r_0)$. The relationship $Eh/r_0$ is based on compliance estimates
\begin{equation}
  \frac{Eh}{r_0} = k_1 \exp \left( k_2 r_0(z) \right) + k_3
\end{equation}
with $k_1, k_2, k_3$ constants \cite{Olufsen2000}. To derive \eqref{eq:conservation} it was necessary to make assumptions about the velocity profile of blood flow through an artery. Blood flow is considered pulsatile laminar and vessels are considered slightly tapered, therefore the velocity profile is assumed to be mostly flat with a thin boundary layer $\delta_b = (\nu T/(2\pi))^{0.5}$, such that $\delta_b \ll R(z,t)$ and $\text{Re} \approx 200$ \cite{Olufsen2000}.

@@

The numerical model of the MCA was run over four heartbeats to ensure convergence of the results. A human heartbeat lasts \SI{0.85}{\second} and the total simulation time was \SI{3.4}{\second}
